A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-03-16 main.tex
TMWH

% Authors, for the paper (add full first names)
\Author{
Li-Hsing Chi $^{1,2}$\orcidA{}, Alexander TH Wu $^{1}$,
Michael Hsiao $^{3}$*
and Yu-Chuan (Jack) Li $^{1,4}$*\orcidB{}}
%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad The Ph.D. Program for Translational Medicine, College of Medical Science and Technology\unskip, 
    Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\
$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\
$^{3}$ \quad Genomics Research Center\unskip, 
    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
$^{4}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
}

@@

%discussion: the third limitation
There are eighty-one ($X_1 ... X_81$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features from holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status. (see Figure \ref{fig:figure5})
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
The second principle is empowering – supporting people to manage and take responsibility for their health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

@@

%% TCGA new holistic features %%%%%
Our current study summarizes those six candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific six gene expressions, clinical T stage, and surgical margin so far.
When we consider the survival prediction model again,
ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\
gene expression is not an independent $X_{mrna}$, which could be correlated with other $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
%We wish the TCGA does collect more holistic features from their participants in the future.
%依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
We suggest TCGA should cover more holistic features:
cortisol is one of the most common objective outcomes studied in psychoneuroimmunological (PNI) factors. Other factors are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}.
%冤親債主的意念 unknown X factors 回到我們的文章
Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.

@@

%https://mos2718.github.io/FHIRspec/Index.html
%https://www.hl7.org/fhir/patient.html
%https://mos2718.github.io/FHIRspec/Spec/Patient/EHR_Patient.docx
In Taipei Medical University Hospital, holistic-enabled EHR has been designed as the holistic dental chart for our outpatient with psycho-social-spiritual evaluation\cite{Ling-ChengMong2021}:\\
1. Emotional: stable/depression/ anxiety/ agitated/ perplexed\\
2. Interaction: expression disorder/ confusion/ hard to make decision/ uncooperative to dental treatment\\
3. Social: (disturbing living/ disturbing working/ disturbing other life aspect) by present illness\\
4. Function loss(subjectively): mastication/ pronunciation/ life quality/ state of mind\\
5. Self-expectation: lack of confidence/ low self-esteem/ social-withdrawal\\
6. Impact to life: financial problem/ family problem\\
7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment/ side-effects/ litigation experience\\[2cm]

In personal history section of admission note for inpatient:\\
<Habits>\\
-Tobacco: \underline{ }\underline{ } pack/day for \underline{ }\underline{ } years\\
-Alcohol drinking: Occasionally\\
-Betel nuts: \underline{ }\underline{ } nuts/day for \underline{ }\underline{ } years\\
<Social/Economic Evaluation>\\
-Living condition: Living with family\\
-Family support: Well\\
-Main caregiver: Spouse\\
-Financial support: Sufficient\\
<Psychological Evaluation>\\
Stable but worry about this oral lesion\\
Suspected to be abuse or neglected victim: negative\\
<Spiritual Assessment>\\
Religion: Nil\\
Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No\\
% cancer cure (care) 的證明
%# 懺悔
We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body's hard working. Mindfulness and meditation will be helpful in cancer healthcare.
Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
%七情: 喜、怒、思、悲、恐、驚、憂

>>>>

% Authors, for the paper (add full first names)
\Author{
Li-Hsing Chi $^{1,2,3}$\orcidA{}, Alexander TH Wu $^{1}$,
Michael Hsiao $^{4}$*
and Yu-Chuan (Jack) Li $^{1,5}$*\orcidB{}}
%\Author{Firstname Lastname $^{1,\dagger,\ddagger}$\orcidA{}, Firstname Lastname $^{1,\ddagger}$ and Firstname Lastname $^{2,}$*}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad The Ph.D. Program for Translational Medicine, College of Medical Science and Technology\unskip, 
    Taipei Medical University and Academia Sinica\unskip, Taipei\unskip, Taiwan\\

%Director,
$^{2}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip, 
    Taipei Municipal Wanfang Hospital\unskip, Taipei\unskip, Taiwan\\

$^{3}$ \quad Division of Oral and Maxillofacial Surgery, Department of Dentistry\unskip,
    Taipei Medical University Hospital\unskip, Taipei\unskip, Taiwan\\

$^{4}$ \quad Genomics Research Center\unskip, 
    Academia Sinica\unskip, Taipei\unskip, Taiwan\\
$^{5}$ \quad Graduate Institute of Biomedical Informatics, College of Medical Science and Technology\unskip, Taipei Medical University\unskip, Taipei\unskip, Taiwan\\
}

@@

%discussion: the third limitation
There are eighty-one ($X_1 ... X_{81}$) physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, 
% since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days\_to\_last\_followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features from holistic cancer care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021} spiritual and emotional condition is equally essential comparing with physical and social status. (see Figure \ref{fig:figure5})
%
World Health Organisation has called worldwide for delivering people-centred (or person-centred) care from the physical, emotional, socioeconomic, and spiritual perspectives\cite{WHO2015}\cite{Ling-ChengMong2021}.
Core principles can be taken to achieve people-centred and integrated health service delivery. 
The first principle is holistic – focusing on physical, socioeconomic, mental, and emotional well-being. 
Holistic care has been defined that care and sees the person as a whole with psychological, social, and environmental levels of needs and goals.
%that considers  factors rather than just the symptoms of disease or ill-health.
The second principle is empowering – supporting people to manage and take responsibility for their health,
%Empowerment: the process of supporting people and communities to take control of their own health needs resulting, 
for example, in the uptake of healthier behaviors or the ability to self-manage illnesses.
People-centred care requires that people have the education and support they need to make decisions and participate in their care.
%Glossary:
%People-centred care: an approach to care that consciously adopts individuals’, carers’, families’ and communities’ perspectives as participants in, and beneficiaries of, trusted health systems that respond to their needs and preferences in humane and holistic ways. People-centred care also requires that people have the education and support they need to make decisions and participate in their own care. It is organized around the health needs and expectations of people rather than diseases (7,8) 
%Person-centred care: care approaches and practices that see the person as a whole with many levels of needs and goals, with these needs coming from their own personal social determinants of health.
%(1. World Health Organization. WHO global strategy on people-centred and integrated health services: interim report. https://apps.who.int/iris/handle/10665/155002 (2015).)

@@

%% TCGA new holistic features %%%%%
Our current study summarizes those six candidate biomarkers, clinical T stage, and surgical margin are independent prognosis factors in our \acrshort{hnscc} study.
Thus, the prognosis model with coefficients is established from \acrshort{tcga} \acrshort{hnscc} cohort. The important input $X_1...X_n$ should be patients' features: age, specific six gene expressions, clinical T stage, and surgical margin so far.
When we consider the survival prediction model again,
ground truth Y (e.x. patient's survival):\\[0.5cm]
%Y$:\\[0.3cm]
$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$\\[0.5cm]
Gene expression is not an independent $X_{mrna}$. It could be correlated with other\\ $X_{body}, X_{stress}, X_{fear}, X_{meaningOfLife}, X_{inflammation}, X_{ros}$ factors.
There is much work to be done in investigating the functional network more fully\cite{Rogers1959}.
%We wish the TCGA does collect more holistic features from their participants in the future.
%依舊是以管窺天
% https://link.springer.com/referenceworkentry/10.1007%2F978-1-4419-1428-6_575
%癌症與身心靈的重要關係：中醫、citation? emotional centered approach
We suggest TCGA should cover more holistic features:
cortisol is one of the most common objective outcomes studied in psychoneuroimmunological (PNI) factors. Other factors are interleukin, cytokines, lymphocytes (CD4+, CD8+), CD56+, vitals signs, telomere length, telomere activity, HRV.
The standardized, psychosocial (subjective) measures include depression, stress, quality of life, anxiety, fatigue, mindfulness, mood, and specific spiritual growth (i.e., the meaning of life)\cite{Hsiao2012}.
%冤親債主的意念 unknown X factors 回到我們的文章
Since psychological benefit (reduction of stress, fatigue, sleep disturbance, and depressive symptoms) also optimizes immune function (higher natural killer cell activity, higher \acrshort{ifng}, lower TNF-alpha, lower IL-6) in terms of better survival of cancer patients.

@@

%https://mos2718.github.io/FHIRspec/Index.html
%https://www.hl7.org/fhir/patient.html
%https://mos2718.github.io/FHIRspec/Spec/Patient/EHR_Patient.docx
In Taipei Medical University Hospital, holistic-enabled EHR has been designed as the holistic dental chart for our outpatient with psycho-social-spiritual evaluation\cite{Ling-ChengMong2021}:\\
1. Emotional: stable/depression/ anxiety/ agitated/ perplexed\\
2. Interaction: expression disorder/ confusion/ hard to make decision/ uncooperative to dental treatment\\
3. Social: (disturbing living/ disturbing working/ disturbing other life aspect) by present illness\\
4. Function loss(subjectively): mastication/ pronunciation/ life quality/ state of mind\\
5. Self-expectation: lack of confidence/ low self-esteem/ social-withdrawal\\
6. Impact to life: financial problem/ family problem\\
7. Medical relationship: bad experience of dental treatment/ loss confidence to dentist/ anxious to treatment/ side-effects/ litigation experience\\[0.5cm]

In personal history section of admission note for inpatient:\\
<Habits>\\
-Tobacco: \underline{ }\underline{ } pack/day for \underline{ }\underline{ } years\\
-Alcohol drinking: Occasionally\\
-Betel nuts: \underline{ }\underline{ } nuts/day for \underline{ }\underline{ } years\\
<Social/Economic Evaluation>\\
-Living condition: Living with family\\
-Family support: Well\\
-Main caregiver: Spouse\\
-Financial support: Sufficient\\
<Psychological Evaluation>\\
Stable but worry about this oral lesion\\
Suspected to be abuse or neglected victim: negative\\
<Spiritual Assessment>\\
Religion: Nil\\
Diagnosed with life-threatening diseases or terminal stage of chronic diseases or cancers? No
% cancer cure (care) 的證明
%# 懺悔

We continually educate our cancer patients that they should repentantly confess for not taking care of body and spirit in the past, and sincere thanks for our physical body's hard working. Mindfulness and meditation will be helpful in cancer healthcare.
Once the holistic feature is available, a graph convolutional neural network (GCNN) is mandatory for further survival analysis\cite{Ching2018a}.
The microenvironment of HNSCC, influenced by the mind-brain-body axis, requires further exploration and understanding using this multi-parametric approach.
%  extreme pleasure, anger, overthinking, sadness, fear, shock, anxiety, depression, fatigue, stress
%七情: 喜、怒、思、悲、恐、驚、憂
